Linear Variation and an Optimization of Algorithms for Connected Components Labeling in a Binary Image

### 2016-04-14 paper/paper.tex
Fix text width

The norm and modulus of the gradient are metrical characteristic of a function
of two variables.
Continuous functions of two variables also have a set of topological
characteristics referred to as linear variations.
Kronrod%\cite{mak2}
introduced the notion of a regular component of the level set of a
continuous function of two variables.
The simplest topological characteristic in the linear variation theory is a
number of regular components for all level sets of a function.
Full information about linear variations of a function is contained in the
one-dimensional tree of a function of two variables.
In \cite{mak3,mak4,mak5}
was discussed the necessity of the using a linear variation in the
image restoration theory.

@@

The test images were generated in the following manner. At first, for given
density $d$, the first $4dNM$ pixels of the $2N \times 2M$ image were filled
with object values, while rest filled with background values. Then all the
pixels were permuted using \texttt{std::shuffle} function from \CXX standard
library, which is an implementation of Fisher-Yates Shuffle
algorithm%\cite{fisher:yates}
.

@@

% \bibitem {mak2}
% Kronrod, A.:
% On functions of two variables.
% Uspehi Mat. Nauk 5, 1(35), 24-134(1950)

@@

\bibitem {mak4}
Makovetskii, A., Kober, V.:
Modified gradient descent method for image restoration.
Proc. SPIE Applications of Digital Image Processing XXXVI, 8856, 885608-1 (2013)

@@

\bibitem {CLRS}
Cormen, H., Leiserson, E., Rivest, L., Stein, C.:
Introduction to Algorithms (Second ed.).
MIT Press (2001)

@@

% \bibitem {fisher:yates}
% Fisher, A., Yates, F.:
% Statistical tables for biological, agricultural and medical research (3rd ed.).
% London: Oliver \& Boyd. pp. 26–27. OCLC 14222135 (1948)

\bibitem{mt19937}
Matsumoto, M., Nishimura, T.:
Mersenne twister: a 623-dimensionally equidistributed uniform pseudo-random
number generator.
ACM Transactions on Modeling and Computer Simulation 8 (1): 3–30. (1998)

>>>>

The norm and modulus of the gradient are metrical characteristic of a function
of two variables.
Continuous functions of two variables also have a set of topological
characteristics referred to as linear variations.
Kronrod\cite{mak2}
introduced the notion of a regular component of the level set of a
continuous function of two variables.
The simplest topological characteristic in the linear variation theory is a
number of regular components for all level sets of a function.
Full information about linear variations of a function is contained in the
one-dimensional tree of a function of two variables.
In \cite{mak3,mak4,mak5}
was discussed the necessity of the using a linear variation in the
image restoration theory.

@@

The test images were generated in the following manner. At first, for given
density $d$, the first $4dNM$ pixels of the $2N \times 2M$ image were filled
with object values, while rest filled with background values. Then all the
pixels were permuted using \texttt{std::shuffle} function from \CXX standard
library, which is an implementation of Fisher-Yates Shuffle
algorithm\cite{fisher:yates}.

@@

\bibitem {mak2}
Kronrod, A.: On functions of two variables ," Uspehi Mat. Nauk 5, 1(35), 24-134(1950)

@@

\bibitem {mak4}
4.	Makovetskii, A., Kober, V.: Modified gradient descent method for image restoration. Proc. SPIE Applications of Digital Image Processing XXXVI, 8856, 885608-1 (2013)

@@

\bibitem {CLRS}
Cormen, H., Leiserson, E., Rivest, L., Stein, C.:
Introduction to Algorithms (Second ed.), MIT Press (2001)

@@

\bibitem {fisher:yates}
 Fisher, A., Yates, F.:
 Statistical tables for biological, agricultural and medical research (3rd ed.). 
 London: Oliver \& Boyd. pp. 26–27. OCLC 14222135 (1948)

\bibitem{mt19937}
Matsumoto, M., Nishimura, T.:
"Mersenne twister: a 623-dimensionally equidistributed uniform pseudo-random number generator".
ACM Transactions on Modeling and Computer Simulation 8 (1): 3–30. (1998)
